Loop Invariant Code Motion in PyPy's Tracing JIT

### 2011-06-13 talk/iwtc11/paper.tex
Copy-paste of the figure subtitle confused me greatly
Try to clarify a confusing para

Loop peeling is achieved prefixing the loop with one iteration of itself. The
peeled of iteration of the loop will end with a jump to the full loop, which
ends with a jump to itself. This way the peeled of iteration will only be
executed once while the second copy will be used for every further iteration.
The trace from Figure~\ref{fig:unopt-trace} would after this operation become
the trace in Figure~\ref{fig:peeled-trace}.

@@

$l_1$($p_{0}$, $p_{5}$):
# inside f: y = y.add(step)
guard_class($p_{5}$, BoxedInteger)
    # inside BoxedInteger.add
    $i_{6}$ = get($p_{5}$, intval)
    guard_class($p_{0}$, BoxedInteger)
        # inside BoxedInteger.add__int
        $i_{7}$ = get($p_{0}$, intval)
        $i_{8}$ = $i_{6}+i_{7}$
        $p_{9}$ = new(BoxedInteger)
            # inside BoxedInteger.__init__
            set($p_{9}$, intval, $i_{8}$)
jump($l_1$, $p_{0}$, $p_{9}$)
\end{lstlisting}
\caption{An Unoptimized Trace of the Example Interpreter}
\label{fig:peeled-trace}
\end{figure}

>>>>

Loop peeling is achieved by copying the traced iteration of the loop.
The first part (called preamble) finishes with the jump the the second part
(peeled loop). The second part ends up with the jump to itself. This way
the preamble will be executed only once while the peeled loop will
be used for every other iteration.
The trace from Figure~\ref{fig:unopt-trace} would after this operation become
the trace in Figure~\ref{fig:peeled-trace}.

@@

$l_1$($p_{0}$, $p_{5}$):
# inside f: y = y.add(step)
guard_class($p_{5}$, BoxedInteger)
    # inside BoxedInteger.add
    $i_{6}$ = get($p_{5}$, intval)
    guard_class($p_{0}$, BoxedInteger)
        # inside BoxedInteger.add__int
        $i_{7}$ = get($p_{0}$, intval)
        $i_{8}$ = $i_{6}+i_{7}$
        $p_{9}$ = new(BoxedInteger)
            # inside BoxedInteger.__init__
            set($p_{9}$, intval, $i_{8}$)
jump($l_1$, $p_{0}$, $p_{9}$)
\end{lstlisting}
\caption{A peeled trace of the Example Interpreter}
\label{fig:peeled-trace}
\end{figure}
